Scalar on Function Regression

### 2022-01-03 Presentation/slides.tex
Some Estimation Stuff

	\begin{frame}{Theory - FPCA}
		Jakob
		\begin{itemize}
			\item Let's assume you know the theory of PCA (pc from varcov matrix)
			\item Introduce mean and covariance functions of random functions
			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion)
			\item Sample Analog! (create a basis from observations and use for basis regression)
			\item Plot fpcs and approximation of function realization
		\end{itemize}
	\end{frame}

@@

		The principal components are then defined analogously to before:
		$$Z_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$

>>>>

	\begin{frame}{Estimation via Basis Representation}
		Assume the following data generating process
		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
		\begin{itemize}
			\item $Y$ and $\epsilon$ realize in $\mathbb{R}$ and $F$ realizes in $\mathbb{L}^2[0,1]$
		\end{itemize}
		\vspace{0.2cm}

		Assume that we have a data set containing observations each of which is made up of:
		\begin{itemize}
			\item $y_i$: \quad a scalar realizations of $Y$
			\item $f_i(t)$: \quad a realization of $F$
		\end{itemize}

	\begin{frame}{Estimation via Basis Representation}
		Let $\{b_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$
		\vspace{0.2cm}

		Then we have the following representation of $\beta(t)$
		$$\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t) = \sum_{j = 1}^{L} \psi_j b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j b_j(t)$$
		and we can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	  
			\end{split}
		\end{equation}
	\end{frame}

	\begin{frame}
		$$\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
		This is a scalar we can calculate for each observation and for each deterministic basis function $b_j(t)$.
	\end{frame}

	\begin{frame}{Theory - FPCA}
		Jakob
		\begin{itemize}
			\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
			\item Introduce mean and covariance functions of random functions $\checkmark$
			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
			\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
			\item Plot fpcs and approximation of function realization
		\end{itemize}
	\end{frame}

@@

		The $\{\hat{\nu}_i(s) \: \vert \: i \in \mathcal{I}\}$ are called \textbf{Functional Principal Components} and can serve as a basis for representing the original curves. 
		\vspace{0.2cm}

		The corresponding scores $\hat{\xi}_i$ can be derived as
		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
